---
title: "Moving beyond theme_gray: Exploring advanced ggplot2 for customized plot layouts"
author: 
  - "Presentation by Emma Skarstein"
date: "October 2021"
output:
  revealjs::revealjs_presentation:
    theme: night
    transition: none
    self_contained: true
    css: slides.css
    incremental: true
  beamer_presentation:
    toc: false
    incremental: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

## Plan

- Look at the data: Tate art collection artwork and artists
- Look at three visualizations

## Dataset: Tate art collection
```{r}
# Get the Data

# Read in with tidytuesdayR package 
# Install from CRAN via: install.packages("tidytuesdayR")
# This loads the readme and all the datasets for the week of interest

tuesdata <- tidytuesdayR::tt_load(2021, week = 3)
artwork <- tuesdata$artwork
artists <- tuesdata$artwork

str(artwork)
head(artists)
```


## Links for the scripts

[Maia Pelletier](https://github.com/MaiaPelletier/tidytuesday/blob/master/R/2021_Week03_TateArt.R)

[Ijeamaka Anyene](https://github.com/Ijeamakaanyene/tidytuesday/blob/master/scripts/2021_02_tate.Rmd)

[Georgios Karamanis](https://github.com/gkaramanis/tidytuesday/blob/master/2021/2021-week2/art-collections.R )


## Github pages of the creators

https://github.com/MaiaPelletier

https://github.com/Ijeamakaanyene

https://github.com/gkaramanis 



## Further resources

- ["Spice up your standard charts", talk by Ijeamaka Anyene](https://www.youtube.com/watch?v=LlVf8foXUmM)
  - Goes more into creating good "basic" plots
  
- Tidyverse cheat sheets: https://www.rstudio.com/resources/cheatsheets/ 

- [BBC Visual and Data Journalism cookbook for R graphics](https://bbc.github.io/rcookbook/)
